---
title: "My Super Spiffy Markdown Thing"
output: markdowntemplates::hrbrmrkdn
---
```{r include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  message = FALSE, warning = FALSE, echo = TRUE, fig.retina = 2, collapse = TRUE
)
knitr::knit_hooks$set(chunk = markdowntemplates:::chunk_hook_html) # DO NOT DELETE - NECESSARY FOR PRISM
knitr::knit_hooks$set(optipng = knitr::hook_optipng) # DELETE ONLY IF YOU DON'T WANT COMPRESSION
knitr::knit_hooks$set(pngquant = knitr::hook_pngquant) # DELETE ONLY IF YOU DON'T WANT COMPRESSION
library(hrbrthemes)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
